Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-01-26 src/sections/intro.tex
Finished first pass introduction, split off some stuff into a modeling section

In addition to the light-element anti-correlations observed it is also known
that younger populations are signifigantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to the relatively high and tight temperature range of partial
ionization for He it cannot be observed in globular clusters; consequently, the
evidence for enhanced He in GCs originates from comparison of theoretical
stellar isochrones to the observed color-magnitude-diagrams of globular
clusters. Therefore, a careful handling of chemistry is essential when modeling
with the aim of discriminating between MPs; yet, only a very limited number of
GCs have yet been studied with chemically self-consistent (structure and
atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.

This thesis will contain chapters where we expand the number of clusters which
have been self-consistently modeled. In this chapter we will focus on
chemically self-consistent modeling of the two extreme population of NGC 2808
identified by \citep{Milone2015}, A and E.

One key element of NGC 2808 modeling is the incorporation of new atmospheric
models, generated from the \texttt{MARCS} grid of model atmospheres \citep{Plez2008},
which match interior elemental abundances. \texttt{MARCS} provides one-dimensional,
hydrostatic, plane-parallel and spherical LTE atmopsheric models
\citep{Gustafsson2008}. Members of our collaboration have generated atmospheric 
models for populations A and E.  Integration of these new model atmospheres
into DSEP is ongoing.

\subsubsection{Population Opacities}
For similar reasons as discussed in \S\ref{sec:p1} we conduct this research
with OPLIB high-temperature opacity tables as opposed to OPAL tables. We will
also generate low temperature opacity tables using the \texttt{MARCS}.
Moreover, we confirm that the atmosphere and structure meet in an optically
thick region of the star by shifting the atmospheric fitting point from an optical
depth of $\tau = 2/3$ (used by DSEP currently for \texttt{PHOENIX} model atmospheres) to
some higher $\tau$. We will experiment to identify the best optical depth to
fit at..

These population have been studied in depth by Feiden and their chemical
compositions were determined in \citet{Milone2015} (see Table 2 in that paper).
While we cannot yet evolve DSEP models with these new boundary conditions, we
can make a first pass investigation of the affect of OPLIB opacities (Figure
\ref{fig:NGC2808ISO}). Note how the models generated using OPLIB opacity tables
have a systematically lower luminosity. This discrepancy is consistent with
the overall lower opacities of the OPLIB tables.

\subsubsection{Additional Consistency}
The isochrones generally used to infer the degree of helium enhancements assume that
convection operates in the same manner in metal-poor stars as it does in the
Sun. However, observations from \textit{Kepler} of metal-poor red giants
\citep{Bonaca2012, tayar2017correlation}, in concert with interferometric
radius determination of the metal-poor sub-giant HD 140283
\citep{creevey2015benchmark}, have shown that the efficiency of convection
changes with iron content. As the final portion of our work to more carefully
handle a star's chemistry, we will modify DSEP to capture this variation in
convective efficiency.

>>>>

In addition to the light-element anti-correlations observed it is also known
that younger populations are signifigantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to the relatively high and tight temperature range of partial
ionization for He it cannot be observed in globular clusters; consequently, the
evidence for enhanced He in GCs originates from comparison of theoretical
stellar isochrones to the observed color-magnitude-diagrams of globular
clusters. Therefore, a careful handling of chemistry is essential when modeling
with the aim of discriminating between MPs; yet, only a very limited number of
GCs have yet been studied with chemically self-consistent (structure and
atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}. Here we present new,
chemically self-consistent modeling og the two extreme populations of NGC 2808
identified by \citet{Milone2015}, A and E.
